Lifting CDCL to Numerical Domains

### 2016-09-29 cdcl.tex
cdcl

\section{Lifting CDCL to numeric domains}
The work of~\cite{dhk2013-popl,sas12,tacas12} shows that 
satisfiability solvers are static analyzers. They present 
a framework that strictly generalizes CDCL algorithm to 
lattices and abstract transformers. We refer the reader 
to~\cite{dhk2013-popl} for a more formal perspective alongwith 
soundness and completeness proofs.  In this section, we focus 
on the practical aspect of lifting CDCL algorithm to numeric 
abstract domains.

We treat programs as a logical formula. Give a programs $P$ and a trace $\pi$,
$\pi \models P$ iff trace $\pi$ is an erroneous trace generated by program
$P$. 
CDCL algorithm has two main phases which feedback information to 
each other -- {\em model search} and {\em conflict analysis}. The model 
search procedure tries to find a satisfying assignment to the input 
formula. If the search fails, meaning that the current partial assignment 
leads to a {\em conflict}, the conflict analysis phase learns the reason 
for such failure to block the model search from entering into same 
conflicting search-space in future. More formally, given a set of 
formula $Form$ and a set of structure $Struct$, a semantic entailment 
relation, $\models \in \mathcal{P}(Struct \times Form)$, identifies the 
structure that satisfies a formula. A concrete domain is the power set 
of structures which gives us lattice. 
We define two transformers for a CDCL solver. \\
\textit{Model Transformer (mod):} Given a set of structure $S$, return all structures 
in $S$ that satisfy a formula $\varphi$. This is formally shows as follows:
$mod_{\varphi}(S) = \{\sigma | \sigma \in S \wedge \sigma \models \varphi\}$ \\

>>>>

\section{Lifting CDCL to numeric domains}
The work of~\cite{dhk2013-popl,sas12,tacas12} shows that 
satisfiability solvers are static analyzers. They present 
a framework that strictly generalizes CDCL algorithm to 
lattices and abstract transformers. We refer the reader 
to~\cite{dhk2013-popl} for a more formal perspective of 
abstract CDCL.  In this section, we focus on the practical 
aspect of lifting CDCL algorithm to numeric (relational and 
non-relational) abstract domains.

We treat programs as a logical formula. Give a programs $P$ and a trace $\pi$,
$\pi \models P$ iff trace $\pi$ is an erroneous trace generated by program
$P$. 
CDCL algorithm has two main phases which alternates between each 
other -- {\em model search} and {\em conflict analysis}. The model 
search procedure tries to find a satisfying assignment to the input 
formula. If the search fails, then the current partial assignment is 
conflicting, that is, it contains only countermodels.  The conflict 
analysis phase derives a generalized reason for conflict which learns a new 
lemma in the form of a clause. The learned clause is used to block the 
model search from entering into same conflicting search-space in future.

More formally, given a set of formula $Form$ and a set of structure $Struct$, a semantic entailment relation, $\models \in \mathcal{P}(Struct \times Form)$, identifies the structure that satisfies a formula. A concrete domain is the power set of structures which gives us lattice. 
We define two transformers for a CDCL solver. \\
\textit{Model Transformer (mod):} Given a set of structure $S$, return all structures 
in $S$ that satisfy a formula $\varphi$. This is formally shows as follows:
$mod_{\varphi}(S) = \{\sigma | \sigma \in S \wedge \sigma \models \varphi\}$ \\
